%A
\def\apj{Astrophys.~J}
\def\apjl{Astrophys.~J.,~Lett}
\def\apjs{Astrophys.~J.,~Suppl.~Ser}
\def\ap{Astrophysics}
\def\an{Astron.~Nachr}
\def\actaa{Acta Astron}
\def\aap{Astron.~Astrophys}
\def\aaps{Astron.~and Astrophys.,~Suppl.~Ser}
\def\aatr{Astron.~Astrophys.~Trans}
\def\aspcs{ASP~Conf.~Ser}
\def\aj{Astron.~J}
\def\araa{Ann.~Rev.~Astron.~Astrophys}
\def\apss{Astrophys.~Space.~Sci}
\def\astl{Astron.~Letters}
\def\aapr{Astron.~Astrophys.~Rev}
\def\acp{Atmosphere~Chem.~Phys}
\def\aph{Astroparticle~Physics}
\def\adspr{Adv.~Space~Res}
\def\arep{Astron.~Rep}
\def\astbu{Astrophys.~Bull}

%B
\def\bicds{Bull.~Inf.~Cent.~de Donn{'e}es Stellaires}
\def\bastic{Bull.~Astron.~Inst.~Czech}
\def\bain{Bull.~Astron.~Inst.~Neth}
\def\bamass{Bull.~Am.~Astron.~Soc}
\def\bott{Bol.~Obs.~Tonantzintla~Tacubaya}
\def\baltas{Baltic~Astron}

%C
\def\cemda{Celest.~Mech.~Dyn.~Astr}
\def\ceab{Cent.~Eur.~Astrophys.~Bull}
\def\cophc{Comput.~Phys.~Commun}
\def\cemec{Celest.~Mech}
\def\cajph{Can.~J.~Phys}
\def\caosp{Contrib.~Astron.~Obs.~Skalnat{\'e}~Pleso}

%E
\def\epsl{Earth~Planet.~Sci.~Lett}
\def\emp{Earth,~Moon~and~Planets}

%G
\def\geoj{Geophys.~J}
\def\gca{Geochim.~Cosmochim.~Acta}

%I
\def\ibvs{Inf.~Bull.~Variable~Stars}
\def\icar{Icarus}

%J
\def\jaavso{J.~Am.~Assoc.~Variable~Star~Obs}
\def\japa{J.~Astrophys.~Astron}
\def\jcp{J.~Chem.~Phys}
\def\jgr{J.~Geophys.~Res}
\def\jcoph{J.~Comp.~Phys}
\def\jrasc{J.~R.~Astron.~Soc.~Can}
\def\jasa{J.~Acoust.~Soc.~Am}
\def\jfm{J.~Fluid~Mech}
\def\jqsrt{J.~Quant.~Spectrosc.~Radiat.~Transfer}
\def\jbasta{J.~Br.~Astron.~Assoc}

%L
\def\lnm{Lect.~Notes~in~Math}

%M
\def\memsai{Mem.~Soc.~Astron.~Ital}
\def\mnras{Mon.~Not.~R.~Astron.~Soc}
\def\mitag{Mitt.~Astron.~Ges}

%N
\def\na{New~Astron}
\def\nar{New~Astron.~Rev}
\def\nat{Nature}
\def\nimpa{Nucl.~Instrum.~Methods~Phys.~Res.,~Sect.~A}

%O
\def\oejv{Open~Eur.~J.~Variable~Stars}

%P
\def\prl{Phys.~Rev.~Lett}
\def\phrva{Phys.~Rev.~A}
\def\pf{Phys.~Fluids}
\def\pasp{Publ.~Astron.~Soc.~Pac}
\def\phpl{Physics~of~Plasmas}
\def\pasj{Publ.~Astron.~Soc.~Jpn}
\def\pasau{Proc.~Astron.~Soc.~Aust}
\def\puasau{Publ.~Astron.~Soc.~Aust}
\def\phr{Phys.~Rep}
\def\pss{Planet.~Space~Sci}
\def\pz{Perem.~Zvezdy}

%Q
\def\qjras{Q.~J.~R.~Astron.~Soc}

%R
\def\rmxaa{Rev.~Mex.~Astron.~Astrofis}

%S
\def\ssr{Space~Sci.~Rev}
\def\sci{Science}
\def\soph{Sol.~Phys}

%T
\def\obs{The Observatory}

%V
\def\va{Vistas~Astron}
%%%%%%%%%%%%
%Russian
\def\cosiss{Космич.~исслед}
\def\vestcpbu{Вестн.~С.-Петерб.~ун-та}
\def\izvvrad{Изв.~вузов.~Радиофизика}
\def\izvans{Изв.~AH~CCCP}
\def\vestvgu{Вестн.~ВолГУ}
\def\avest{Астрон.~вест}
\def\azh{Астрон.~журн}
\def\pazh{Письма~в~Астрон.~журн}

%%%%%%%%%%%%
\def\thmc{Тез.~международ.~конф}
\def\mmc{Материалы~международ.~конф}
\def\mvrc{Материалы~всерос.~конф}
\def\cntc{Сб.~науч.~тр.~конф}
\def\tmnpc{Тр.~Международ.~науч.-практ.~конф}
\def\ctc{Сб.~тр.~конф}
\def\mcnctone{Тр.~31-й~Международ.~студ.~науч.~конф., Екатеринбург, 28 янв. --- 1 февр. 2002~г}
\def\mcnctto{Тр.~43-й~Международ.~студ.~науч.~конф., Екатеринбург, 3 --- 7 февр. 2014~г}
\def\mcncttr{Тр.~44-й~Международ.~студ.~науч.~конф., Екатеринбург, 2 --- 6 февр. 2015~г}
\def\mcnctfo{Тр.~34-й~Международ.~студ.~науч.~конф., Екатеринбург, 31 янв. --- 4 февр. 2005~г}
\def\mcnctfi{Тр.~35-й~Международ.~студ.~науч.~конф., Екатеринбург, 30 янв. --- 3 февр. 2006~г}
\def\mcnctsi{Тр.~36-й~Международ.~студ.~науч.~конф., Екатеринбург, 29 янв. --- 2 февр. 2007~г}
\def\mcnctse{Тр.~37-й~Международ.~студ.~науч.~конф., Екатеринбург, 28 янв. --- 1 февр. 2008~г}
\def\mcncfo{Тр.~40-й~Международ.~студ.~науч.~конф., Екатеринбург, 31 янв. --- 4 февр. 2011~г}
\def\tmc{Тр.~Международ.~конф}
\def\tmac{Тр.~Международ.~астрон.~конф}
\def\tc{Тр.~конф}
\def\thc{Тез.~конф}

\def\IAUsymp{Proc.~IAU~Symp.}
\def\IAUcoll{Proc.~IAU~Colloquia}
\def\prconf{Proc.~conf.}
\def\aspproc{Proc.~ASP~conf.~ser.}
\def\aipproc{Proc.~AIP~conf.~ser.}
\def\princonf{Proc.~int.~conf.}
